Spin-orbit misalignment for the long period companion of KOI-368

### 2013-06-26 msV0.tex
added figures
add in some text in intro and method, add in references.

\documentclass[apjl]{emulateapj}

\shorttitle{shorttitle}
\shortauthors{shortauthors}

@@

@@

@@

% Figure X plots

>>>>

\documentclass[preprint]{emulateapj}
\input{newcommand_gen.tex}
\shorttitle{shorttitle}
\shortauthors{shortauthors}

@@

%Kepler Obliquity measurement
%\citet{Hirano:2012} 
using the rotation period from the lightcurve and 
then combined with the projected rotation period and stellar radius from 
high-res spectrospcopy, measured the obliquity of 15 KOI systems.

%\citet{Barnes:2011} 
use the asymmetry in the Kepler transit lightcurve of KOI-13 to measure 
the spin-obital alignment angle.

@@

{\bf KOI-368} is assigned as Kepler Object of Interesting in the 
Batalha:2013 
from the Quarter 1-6 data. It has a Kepler Input Catalog entry 6603043. 
The KIC parameters of the star are $T_{\rm eff} = 9034 {\rm K}$,  
$\rm logg=4.133$, and $\rm FeH = -0.028$, indicating it is a hot and 
fast rotating star. 
The transit parameter from Kepler catalog is $P = 110.3216019 day$, 
$R=19.16$\rearth.
We make use of the public Kepler Long Cadence (29.4min) (Q1-Q15) and 
Short Cadence (59.s?) data (Q8-Q9) to study the photometry effect 
predicted by 
%\citet{Barnes:2009}
The long cadence data consist of 11 transit althogether (assigned transit 
number from epoch 0-11, with the 7th missing). The short cadence data 
cover transit 5 and 6.

For transit fitting, we use the $\rm SAP\_FLUX$, the out of transit 
variations are corrected by the following steps (\ref):

a) removal of bad data points;

b) correction of safe mode and tweaks;

c) a set of cosine functions with minimum period of 1 day.

d) a 7th order polynomial fit on the out of transit parts.

For analysis of the rotation period of the star, we use the $\rm PDC\_FLUX$ 
(\ref) (Q1-Q?).

{\bf TBD: the figure of the lightcurve itself?}

%The gravity darkening model

The gravity darkening model is generatied following 
%\citet{Barnes:2009}
The temperature profile on the stellar surface is determined by the local 
effective gravity.
\begin{equation}
\frac{T}{T_{\rm pole}} \propto (\frac{g_{\rm eff}}{g_{\rm pole}})^{\beta}. 
= F_{f,w} (r,\theta)
\end{equation}
f is the oblation of the star, (definition?), w is the nondimension 
measure of the rotation rate, r and \theta are the normalized the position 
parameters.
The gravity darkening parameter $\beta$ is obtained by xxx.

% \begin{figure}[h!]
%   \centering
%   \includegraphics[width=5cm]{obliq_model.eps}
%   \caption{caption}
%   \label{fig:obliq_model}
% \end{figure}
\begin{figure}
  \centering
  \includegraphics[width=9cm]{obliq_model.eps}
  \caption{caption}
  \label{fig:obliqmodel}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=9cm]{lightcurve.eps}
  \caption{caption}
  \label{fig:lightcurve}
\end{figure}
